### 2018-01-02 article.tex
typo

\subsection{External Users}
External users of the annual report include present and potential investors (equity owners), employees of the company, lenders of funds, customers, suppliers, government agencies and other members of the public: 
\begin{itemize}
\item \textbf{Investors.} The providers of risk capital and their advisers are concerned with the risk inherent in, and return provided by, their investments.  They need information to help them determine whether they should buy, hold or sell.  Shareholders are also interested in information that enables them to assess the ability of the enterprise to pay dividends. 
\item \textbf{Employees.} Employees and their representative groups are interested in information about the stability and profitability of their employers.  They are also interested in information which enables them to assess the ability of the enterprise to provide remuneration, retirement benefits and employment opportunities. 
\item \textbf{Lenders.} Lenders are interested in information that enables them to determine whether their loans, and the interest attaching to them, will be paid when due. 
\item \textbf{Suppliers and other trade creditors.} Suppliers and other creditors are interested in information that enables them to determine whether amounts owing to them will be paid when due. Trade creditors are likely to be interested in an enterprise over a shorter period than lenders unless they are dependent upon the continuation of the enterprise as a major customer. 
\item \textbf{Customers.} Customers have an interest in information about the continuance of an enterprise, especially when they have a long-term involvement with, or are dependent on, the enterprise. 
\item \textbf{Governments and their agencies.} Governments and their agencies are interested in the allocation of resources and, therefore, the activities of enterprises.  They also require information in order to regulate the activities of enterprises, determine taxation policies and as the basis for national income and similar statistics. 
\item \textbf{Public.} Enterprises affect members of the public in a variety of ways.  For example, enterprises may make a substantial contribution to the local economy in many ways including the number of people they employ and their patronage of local suppliers.  Financial statements may assist the public by providing information about the trends and recent developments in the prosperity of the enterprise and the range of its activities.
\end{itemize}
While the objective of annual reports is to provide information about the financial position, performance and changes in financial position of an enterprise, it cannot cater to all the information needs of users. However, as investors are providers of risk capital to the enterprise, financial information from the annual report that meet their needs will also meet the common needs of other users.

@@

\subsubsection{Appointment of New Directors}
\subsubsection{Directors’ Remuneration}
In 2016, JD paid an aggregate of approximately RMB12.7 million (US\$1.8 million) in cash to their executive officers, and approximately US\$0.2 million in cash to their non-executive directors. They have not set aside or accrued any amount to provide pension, retirement or other similar benefits to their executive officers and directors\footnote{See JD.com, Inc. annual report 2016, Page 115}.
The details of remuneration are not mentioned in the report.

@@

\subsection{Audit Committee}
JD’s audit committee consists of Louis T. Hsieh, Ming Huang and David Daokui Li. Mr. Hsieh is the chairman of their audit committee.
The audit committee oversees JD’s accounting and financial reporting processes and the audits of the financial statements of our company.
The audit committee is responsible for, among other things:
\begin{itemize}
\item Appointing the independent auditors and pre-approving all auditing and non-auditing services permitted to be performed by the independent auditors;
\item Reviewing with the independent auditors any audit problems or difficulties and management’s response;
\item Discussing the annual audited financial statements with management and the independent auditors;
\item Reviewing the adequacy and effectiveness of our accounting and internal control policies and procedures and any steps taken to monitor and control major financial risk exposures;
\item Reviewing and approving all proposed related party transactions;
\item Meeting separately and periodically with management and the independent auditors;
\item Monitoring compliance with our code of business conduct and ethics, including reviewing the adequacy and effectiveness of our procedures to ensure proper compliance.
\end{itemize}

\subsection{Nominating and Corporate Governance Committee}
JD’s nominating and corporate governance committee consists of David Daokui Li and Louis T. Hsieh. Mr. Li is the chairperson of their nominating and corporate governance committee. The nominating and corporate governance committee is responsible for, among other things:
\begin{itemize}
\item	Selecting and recommending to the board nominees for election by the shareholders or appointment by the board;
\item	Reviewing annually with the board the current composition of the board with regards to characteristics such as independence, knowledge, skills, experience and diversity;
\item	Making recommendations on the frequency and structure of board meetings and monitoring the functioning of the committees of the board;
\item	Advising the board periodically with regards to significant developments in the law and practice of corporate governance as well as our compliance with applicable laws and regulations, and making recommendations to the board on all matters of corporate governance and on any remedial action to be taken.
\end{itemize}

@@

\subsection{Independent Auditors}
Mr. Hsieh, Mr. Huang and Mr. Li in the company’s audit committee satisfy the “independence” requirements of NASDAQ and Rule 10A-3 under the Securities Exchange Act of 1934. It provides service as states in 3.1.

@@

Turnover represents online direct sales, services and others. The Group’s turnover is as follows:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcccc}
			\toprule
			 &\textbf{2015}&\textbf{2016}&\textbf{Absolute change}&\textbf{Ralative change}\\

@@

The Group recognizes revenues from advertising placements ratably over the period during which the advertising services are provided or on the number of times that the advertisement has been displayed based on cost per thousand impressions, and recognizes revenues from pay for performance marketing services based on effective clicks.

@@

The retained earnings are as follows:

@@

\renewcommand{\arraystretch}{0.83}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}rrrr}
			\toprule 
			& \multicolumn{2}{c}{\textbf{Ordinary shares}} & \multicolumn{2}{c}{\textbf{Treasury stock}} \\\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{Shares}&Amount&\multicolumn{1}{c}{Shares}&\multicolumn{1}{c}{Amount}\\
		\midrule
		\rowcolor[gray]{.96}	
		Balance as of
		December 31,
		2015&2,793,756,650&358&(51,766,164)&(3)\\
		Issuance of ordinary shares&144,952,250&19&-&-\\
		\rowcolor[gray]{.96}
		Surrender of ordinary shares by certain	shareholder&(1)&-&-&-\\
		Exercise of sharebased	awards&-&-&2,820,648&77,496\\
		\rowcolor[gray]{.96}
		Share-based	compensation and vesting of sharebased	awards&-&-&8,812,582&78,903\\
		Balance as of December 31, 2016&2,938,708,899&377&(102,264,502)&(5,181,880)\\
		\bottomrule
		\end{tabular}
	\end{center}
	\caption{Share capital (amounts in thousands of RMB \textyen, shares in one)}\label{table:1}
\end{table}

@@

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&(37.46\%)&(25.51\%)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}
The quick ratio reflects the ability of a company to repay its short-term obligations with its more liquid assets.

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Net cash provided by operating activities&	1,696,322&	8,767,017\\
			Net cash used in investing activities&	(5,790,525)&	(48,268,577)\\
			Net cash provided by financing activities&	(4,700,273)	&(40,699,471)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Net cash flows (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\section{Conclusion}
The Company had a better financial year in 2016 than 2015. Its turnover grew estimate 43.5 percent. Despite the high increase in revenue, JD still suffered net loss in 2016. The main reason of JD’s negative profit is the high expenses. Cost of revenue was more than 80\% in both 2015 and 2016, which accounted for its negative profit. Another expense is fulfillment which accounted for nearly 10\% of its expenses. In spite of the fact that JD suffered annual losses since it listed, it enlarged its market share as online retailer. Its managements also show strong confidence to their ability to further increase and leverage their scale of business.

@@

\newpage
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}

>>>>

\subsection{External Users}
External users of the annual report include present and potential investors (equity owners), employees of the company, lenders of funds, customers, suppliers, government agencies and other members of the public\footnote{CCDG – FRS Framework for the Preparation and Presentation of Financial Statements, Para 5}: 
\begin{itemize}
\item \textbf{Investors.} The providers of risk capital and their advisers are concerned with the risk inherent in, and return provided by, their investments.  They need information to help them determine whether they should buy, hold or sell.  Shareholders are also interested in information that enables them to assess the ability of the enterprise to pay dividends. 
\item \textbf{Employees.} Employees and their representative groups are interested in information about the stability and profitability of their employers.  They are also interested in information which enables them to assess the ability of the enterprise to provide remuneration, retirement benefits and employment opportunities. 
\item \textbf{Lenders.} Lenders are interested in information that enables them to determine whether their loans, and the interest attaching to them, will be paid when due. 
\item \textbf{Suppliers and other trade creditors.} Suppliers and other creditors are interested in information that enables them to determine whether amounts owing to them will be paid when due. Trade creditors are likely to be interested in an enterprise over a shorter period than lenders unless they are dependent upon the continuation of the enterprise as a major customer. 
\item \textbf{Customers.} Customers have an interest in information about the continuance of an enterprise, especially when they have a long-term involvement with, or are dependent on, the enterprise. 
\item \textbf{Governments and their agencies.} Governments and their agencies are interested in the allocation of resources and, therefore, the activities of enterprises.  They also require information in order to regulate the activities of enterprises, determine taxation policies and as the basis for national income and similar statistics. 
\item \textbf{Public.} Enterprises affect members of the public in a variety of ways.  For example, enterprises may make a substantial contribution to the local economy in many ways including the number of people they employ and their patronage of local suppliers.  Financial statements may assist the public by providing information about the trends and recent developments in the prosperity of the enterprise and the range of its activities.
\end{itemize}
While the objective of annual reports is to provide information about the financial position, performance and changes in financial position of an enterprise, it cannot cater to all the information needs of users. However, as investors are providers of risk capital to the enterprise, financial information from the annual report that meet their needs will also meet the common needs of other users.

@@

\subsubsection{Appointment of New Directors}
None.

\subsubsection{Directors’ Remuneration}
In 2016, JD paid an aggregate of approximately RMB12.7 million (US\$1.8 million) in cash to their executive officers, and approximately US\$0.2 million in cash to their non-executive directors. They have not set aside or accrued any amount to provide pension, retirement or other similar benefits to their executive officers and directors\footnote{See JD.com, Inc. annual report 2016, Page 115}.
The details of remuneration are not mentioned in the report.

@@

\subsection{Audit Committee}
JD’s audit committee consists of Louis T. Hsieh, Ming Huang and David Daokui Li. Mr. Hsieh is the chairman of their audit committee\footnote{See JD.com, Inc. annual report 2016, Page 118}.

The audit committee oversees JD’s accounting and financial reporting processes and the audits of the financial statements of our company.
The audit committee is responsible for, among other things:
\begin{itemize}
\item Appointing the independent auditors and pre-approving all auditing and non-auditing services permitted to be performed by the independent auditors;
\item Reviewing with the independent auditors any audit problems or difficulties and management’s response;
\item Discussing the annual audited financial statements with management and the independent auditors;
\item Reviewing the adequacy and effectiveness of our accounting and internal control policies and procedures and any steps taken to monitor and control major financial risk exposures;
\item Reviewing and approving all proposed related party transactions;
\item Meeting separately and periodically with management and the independent auditors;
\item Monitoring compliance with our code of business conduct and ethics, including reviewing the adequacy and effectiveness of our procedures to ensure proper compliance.
\end{itemize}

\subsection{Nominating and Corporate Governance Committee}
JD’s nominating and corporate governance committee consists of David Daokui Li and Louis T. Hsieh. Mr. Li is the chairperson of their nominating and corporate governance committee. The nominating and corporate governance committee is responsible for, among other things\footnote{See JD.com, Inc. annual report 2016, Page 119}:
\begin{itemize}
\item	Selecting and recommending to the board nominees for election by the shareholders or appointment by the board;
\item	Reviewing annually with the board the current composition of the board with regards to characteristics such as independence, knowledge, skills, experience and diversity;
\item	Making recommendations on the frequency and structure of board meetings and monitoring the functioning of the committees of the board;
\item	Advising the board periodically with regards to significant developments in the law and practice of corporate governance as well as our compliance with applicable laws and regulations, and making recommendations to the board on all matters of corporate governance and on any remedial action to be taken.
\end{itemize}

@@

\subsection{Independent Auditors}
Mr. Hsieh, Mr. Huang and Mr. Li in the company’s audit committee satisfy the “independence” requirements of NASDAQ and Rule 10A-3 under the Securities Exchange Act of 1934. It provides service as stated in 3.1.

@@

Turnover represents online direct sales, services and others. The Group’s turnover is as follows\footnote{See JD.com, Inc. annual report 2016, Page F5}:
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lcccc}
			\toprule
			 &\textbf{2015}&\textbf{2016}&\textbf{Absolute change}&\textbf{Ralative change}\\

@@

The Group recognizes revenues from advertising placements ratably over the period during which the advertising services are provided or on the number of times that the advertisement has been displayed based on cost per thousand impressions, and recognizes revenues from pay for performance marketing services based on effective clicks\footnote{See JD.com, Inc. annual report 2016, Page F25, F26}.

@@

The retained earnings are as follows\footnote{See JD.com, Inc. annual report 2016, Page F10}:

@@

The change in the capital for the year as well as the number of shares issued is shown as follows:
\renewcommand{\arraystretch}{0.83}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}rrrr}
			\toprule 
			& \multicolumn{2}{c}{\textbf{Ordinary shares}} & \multicolumn{2}{c}{\textbf{Treasury stock}} \\\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{Shares}&Amount&\multicolumn{1}{c}{Shares}&\multicolumn{1}{c}{Amount}\\
		\midrule
		\rowcolor[gray]{.96}	
		Balance as of
		December 31,
		2015&2,793,756,650&358&(51,766,164)&(3)\\
		Issuance of ordinary shares&144,952,250&19&-&-\\
		\rowcolor[gray]{.96}
		Surrender of ordinary shares by certain	shareholder&(1)&-&-&-\\
		Exercise of sharebased	awards&-&-&2,820,648&77,496\\
		\rowcolor[gray]{.96}
		Share-based	compensation and vesting of sharebased	awards&-&-&8,812,582&78,903\\
		Balance as of December 31, 2016&2,938,708,899&377&(102,264,502)&(5,181,880)\\
		\bottomrule
		\end{tabular}
	\end{center}
	\caption{Share capital (amounts in thousands of RMB \textyen, shares in one)}\label{table:1}
\end{table}

Only one shareholder, Liu Qiangdong, holds more than 50\% of the Group’s shares, with every other shareholder's share less than 5\%.

@@

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&(37.46\%)&(25.51\%)\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}
The quick ratio reflects the ability of a company to repay its short-term obligations with its more liquid assets. It suggests the Group's worse solvency, which is risky for creditors.

@@

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			&\textbf{2015}&\textbf{2016}\\
			\midrule
			Net cash provided by operating activities&	1,696,322&	8,767,017\\
			Net cash used in investing activities&	(5,790,525)&	(48,268,577)\\
			Net cash provided by financing activities&	4,700,273	&40,699,471\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Net cash flows (in thousands of RMB \textyen)}\label{table:1}
\end{table}

@@

\section{Industry Comparison with Ratio Analysis }

\subsection{Short-Term Solvency and Liquidity}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}cccc}
			\toprule 
			& \multicolumn{2}{c}{\textbf{JD.com}} & \multicolumn{1}{c}{\textbf{Amazon}}&\multicolumn{1}{c}{\textbf{Alibaba}}\\\cmidrule(lr){2-3} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{2015}&2016&\multicolumn{1}{c}{2016}&\multicolumn{1}{c}{2016}\\
			\midrule	
			Current Ratio&	1.19&	1.02&	1.04&	2.58\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Liquidity ratios}\label{table:1}
\end{table}

From 2015 to 2016, JD’s current ratio is decreasing. Compared with the industries, JD is the same with Amazon, but much lower than Alibaba. In short, JD need to increase its Short-term Liquidity.

\subsection{Long-Term Solvency}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}cccc}
			\toprule 
			& \multicolumn{2}{c}{\textbf{JD.com}} & \multicolumn{1}{c}{\textbf{Amazon}}&\multicolumn{1}{c}{\textbf{Alibaba}}\\\cmidrule(lr){2-3} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{2015}&2016&\multicolumn{1}{c}{2016}&\multicolumn{1}{c}{2016}\\
			\midrule	
			Financial Leverage Ratios&2.22&	3.78&	4.53&1.52\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Financial leverage ratios}\label{table:1}
\end{table}

From 2015 to 2016, JD’s Financial leverage ratios is much higher, which indicates that JD invests a lot by leverage. Compared with the industries, JD is lower than Amazon, but higher than Alibaba. It seems that JD’s Long-term Liquidity is suitable.

\subsection{Asset Utilization}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}cccc}
			\toprule 
			& \multicolumn{2}{c}{\textbf{JD.com}} & \multicolumn{1}{c}{\textbf{Amazon}}&\multicolumn{1}{c}{\textbf{Alibaba}}\\\cmidrule(lr){2-3} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{2015}&2016&\multicolumn{1}{c}{2016}&\multicolumn{1}{c}{2016}\\
			\midrule	
		Total Assets Turnover &	2.39&	2.12&	1.84&	0.33\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Financial leverage ratios}\label{table:1}
\end{table}

From 2015 to 2016, JD’s Total Assets Turnover decrease slightly, but compared with the industries, JD is still higher than Amazon and Alibaba. It seems that JD’s ability of asset utilization is excellent.

\subsection{Profitability}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}cccc}
			\toprule 
			& \multicolumn{2}{c}{\textbf{JD.com}} & \multicolumn{1}{c}{\textbf{Amazon}}&\multicolumn{1}{c}{\textbf{Alibaba}}\\\cmidrule(lr){2-3} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{2015}&2016&\multicolumn{1}{c}{2016}&\multicolumn{1}{c}{2016}\\
			\midrule	
		Net margin&	-0.05&	-0.01&	0.02&	0.70\\
		ROE&	-0.27&	-0.11&	0.15&	0.35\\
		EPS(US\$)&	-0.53&	-0.20&	4.90&	4.33\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Profitability ratios}\label{table:1}
\end{table}
From 2015 to 2016, JD’s profitability is becoming better, though its net income is still negative. Compared with the industries, Amazon and Alibaba both have achieved profitability. It seems that JD still have a big potentiality.
\subsection{Market Value}

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{p{5.6cm}cccc}
			\toprule 
			& \multicolumn{2}{c}{\textbf{JD.com}} & \multicolumn{1}{c}{\textbf{Amazon}}&\multicolumn{1}{c}{\textbf{Alibaba}}\\\cmidrule(lr){2-3} 
			\multirow{-2}{*}{} &\multicolumn{1}{c}{2015}&2016&\multicolumn{1}{c}{2016}&\multicolumn{1}{c}{2016}\\
			\midrule	
	     	Price-Earnings Ratio&-&-&	49.18&	292.06\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Market value ratios}\label{table:1}
\end{table}
The high Market-Value Ratio indicates the investors believe the this industry will be more valuable in the future.

\section{Conclusion}
JD is the largest e-commerce company in China and the largest Chinese retailer, both in terms of revenue, in 2016. Its turnover grew approximately 43.5 percent. Despite the high increase in revenue, JD still suffered net loss in 2016. The main reason of JD’s negative profit is the high expenses. Cost of revenue was more than 80\% in both 2015 and 2016, which accounted for its negative profit. Another expense is fulfillment which accounted for nearly 10\% of its expenses. In spite of the fact that JD suffered annual losses since it listed, it enlarged its market share as online retailer. Its managements also show strong confidence to their ability to further increase and leverage their scale of business.

@@

\newpage
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
Reference resources: Form 20-F - Annual and transition report of foreign private issuers, SEC Accession No. 0001104659-17-028187

\url{https://www.sec.gov/Archives/edgar/data/1549802/000110465917028187/0001104659-17-028187-index.htm}
